Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits

### 2025-01-26 paper.tex
fix
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>
fix: title
Signed-off-by: Thomas Mauran <thomasmauran@yahoo.com>

% Title and Author
\title{Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits}
\author{Thomas Mauran \\\small Polytech Montpellier  \\\small thomas.mauran@etu.umontpellier.fr}
\date{\today}

@@

% Abstract
\begin{abstract}
Amateur astronomers have increasingly contributed to astronomical research through advancements in affordable equipment and accessible software. This paper investigates the precision and reliability of photometric observations of binary star transits conducted by amateur astronomers compared to data collected by professional observatories. We analyze case studies, compare methodologies, and assess the implications for collaborative scientific research.
\end{abstract}

@@

% Introduction
\section{Introduction}
In recent years, the field of astronomy has witnessed a growing collaboration between amateur 
and professional astronomers. The advent of high-quality, low-cost equipment has enabled 
amateur astronomers to perform sophisticated observations, including photometric studies of 
binary star transits. This paper focuses on photometric observations of the U Cephei 
(U Cephei) binary star system conducted by the author using personal equipment from a 
Bortle 7 location. The study aims to examine the precision and reliability of these amateur 
observations in comparison to professional datasets, exploring the potential for collaboration
and the challenges inherent in combining data from diverse sources. The final goal of the study if it is 
successful enough is to submit the collected data to the AAVSO (American Association of Variable Star Observers).

>>>>

% Title and Author
\title{Assessing the Scientific Value of Amateur Photometric Observations of Binary Star Transits}
\author{Thomas Mauran \\\small Université de Montpellier, Polytech Montpellier \\\small thomasmauran@yahoo.com}
\date{\today}

@@

% Abstract
\begin{abstract}
Amateur astronomers have increasingly contributed to astronomical research through advancements in affordable equipment and accessible software. This paper investigates the precision and reliability of photometric observations of binary star transits conducted by amateur astronomers compared to data collected by professional observatories. We analyze case studies, compare the collected data to professional ones to measure the accuracy of the observations.
\end{abstract}

@@

% Introduction
\section{Introduction}
In recent years, the field of astronomy has witnessed a growing collaboration between amateur 
and professional astronomers. The advent of high-quality, low-cost equipment has enabled 
amateur astronomers to perform sophisticated observations, including photometric studies of 
binary star transits. This paper focuses on photometric observations of the U Cephei 
(U Cephei) binary star system conducted by the author using personal equipment from a 
Bortle 7 location. The study aims to examine the precision and reliability of these amateur 
observations in comparison to professional datasets, exploring the potential for collaboration
and the challenges inherent in combining data from diverse sources.
